---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# gothiclockpicker

<!-- badges: start -->
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://lifecycle.r-lib.org/articles/stages.html#experimental)
[![R-CMD-check](https://github.com/szego/gothiclockpicker/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/szego/gothiclockpicker/actions/workflows/R-CMD-check.yaml)
<!-- badges: end -->

gothiclockpicker finds optimal solutions to the lockpicking puzzles in the
video game *Gothic 1 Remake*.

A lock has several pins, each sitting in their own shackle. Every operation
(sliding a shackle) shifts the selected pin and other pins in the lock by either
left or right. The aim is to bring all pins to their center position. Given the
starting positions and the effect of each shackle  slide, `pick_lock()` returns
a shortest sequence of moves that solves the lock. By default it finds the
solution that minimizes switching between shackles, which tends to be the
easiest to perform in game.

## Installation

You can install the development version of gothiclockpicker from
[GitHub](https://github.com/szego/gothiclockpicker) with:

``` r
# install.packages("remotes")
remotes::install_github("szego/gothiclockpicker")
```

## Example

```{r example}
library(gothiclockpicker)

# A lock with four pins. Each list element is the effect of one operation.
start <- c(-3, 3, -3, 0)
ops <- list(
  c(1, 0, 0, 0),
  c(1, -1, 0, 1),
  c(-1, 0, 1, 0),
  c(0, 0, 0, 1)
)

pick_lock(start, ops)
```

Each step shows the shackle to use and its direction (`+`/`-`), and consecutive
repeats of the same operation are grouped together.
